\Title

### 2015-11-01 manuscript.tex
Tweaks to parametrization

In potential field methods,
we must isolate the target anomalous density distribution prior to modeling and
inversion.
In our case, the target is the relief of the real Moho undulating around a
reference Moho.
We do this by removing all other effects from the gravity observations.
The first correction is to remove the
scalar gravity of an ellipsoidal reference Earth (the Normal Earth),
hereafter denoted as $\gamma$.
This effect is calculated on the same point $P$ where the observation was made
using the closed-form solution presented by \citet{li_2001}.
The difference between the observed gravity ($g$) and Normal gravity
is known as the gravity disturbance,

@@

We parameterize the forward problem by discretizing the Moho undulation
into a grid of $M_{lon} \times M_{lat} = M$ juxtaposed tesseroids
(Fig.~\ref{fig:tesseroid}).
In cases where the Moho is above the reference depth ($z_{ref}$),
the top of the tesseroid is the Moho depth at the location of the $k$-eth
tesseroid ($z_{k}$),
the bottom is $z_{ref}$, and the density-contrast is positive.
If the Moho is below the $z_{ref}$, the top of the tesseroid is $z_{ref}$,
the bottom is the Moho depth, and the density-contrast is negative.

@@

\noindent in which $d_i$ is the $i$th element of the $N$-dimensional predicted
data vector $\mathbf{d}$, $\mathbf{p}$ is the $M$-dimensional parameter vector
containing the Moho depths ($z_k$),
and $f_i$ is the $i$th non-linear function that maps the parameters onto the
data.
$f_i$ is the radial component of the gravitational attraction of the tesseroid
model of the anomalous Moho.

>>>>

In potential field methods,
we must isolate the target anomalous density distribution prior to modeling and
inversion.
In our case, the target is the relief of the real Moho undulating around a
reference Moho.
We do this by removing all other effects from the gravity observations.
The first correction is to remove the
scalar gravity of an ellipsoidal reference Earth (the Normal Earth),
hereafter denoted as $\gamma$.
This effect is calculated on the same point $P$ where the observation was made
using the closed-form solution presented by \citet{li_2001}.
The difference between the observed gravity ($g$) and Normal gravity
is known as the gravity disturbance,
\todo{Figura do seminário acompanha}

@@

We parameterize the forward problem by discretizing the Moho undulation
into a grid of $M_{lon} \times M_{lat} = M$ juxtaposed tesseroids.
In cases where the Moho is above the reference depth ($z_{ref}$),
the top of the tesseroid is the Moho depth at the location of the $k$-eth
tesseroid ($z_{k}$),
the bottom is $z_{ref}$, and the density-contrast is positive.
If the Moho is below the $z_{ref}$, the top of the tesseroid is $z_{ref}$,
the bottom is the Moho depth, and the density-contrast is negative.
\todo{Figura do seminário}

@@

\noindent in which $d_i$ is the $i$th element of the $N$-dimensional predicted
data vector $\mathbf{d}$, $\mathbf{p}$ is the $M$-dimensional parameter vector
containing the $M$ Moho depths ($z_k$),
and $f_i$ is the $i$th non-linear function that maps the parameters onto the
data.
The functions $f_i$ are the radial component of the gravitational attraction
of the tesseroid Moho model.
